---
title: "Test"
author: "Margaret"
date: "31 October 2017"
output: 
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#options(encoding = "native.enc")  #to print Chinese
library(knitr)
```
##Introduction
This is a test of *English as Second Language* for Grade 7 students. This is a pilot test for the purpose of evaluating test items for their psychometric properties so that a final test form can be constructed based on the results of this pilot test. 

The test consists of `r length(mcq)` multiple-choice questions and `r length(key)-length(mcq)` short response questions. Most items are scored dichotomously (0,1) while some items have partial credit scoring (0,1,2).

In total, `r nrow(resp)` students took the test. The test reliability is `r round(alpha,2)`.

<!--- These are for html output file --->
<style type="text/css">
.table {
    width: 40%;
}
</style>
<center>


##Classical Test Theory Item Statistics
```{r results = 'asis', echo=FALSE, warning=FALSE}
discA <- as.integer(disc*100+0.5)  #these lines are for adding "*" and fixing two decimal places.
discB <- round(disc,2)
discB[(discA%%10)==0] <- paste(discB[(discA%%10)==0],"0",sep='')
discB[disc<0.2] <- paste("*",discB[disc<0.2],sep='')
itemstats <- data.frame(round(itemdiff,2),discB)
colnames(itemstats) <- c("Difficulty (%correct)","Discrimination(CTT)")
```
##Item difficulty and discrimination 
```{r echo=FALSE, comment=NA, warning=FALSE}
#itemstats
kable(itemstats,align = 'cc') 
```

##The following is an Item-Person map, also known as the Wright Map
```{r echo=FALSE, message=FALSE,fig.height=8,fig.width=10}
library(WrightMap)
par(ps=14,cex=1.2)  #adjust font size. ps is for axis title's point size. cex enlarges fonts of labels
  p<-wrightMap(Ability,thr,item.side=itemClassic)
```

##Item distractor analysis
```{r echo=FALSE, comment=NA, message=FALSE, warning=FALSE}
for (i in 1:ncol(resp_raw)){
  itemi <- ctt_raw[ctt_raw$Item==colnames(resp_raw)[i],]
  keyc <- rep(" ",length(itemi$Category))
  if(key[i]!="p"){
    keyc[paste(itemi$Category)==rep(key[i],length(itemi$Category))] <- "*"
    itemi$Category <- paste(cname[as.integer(paste(itemi$Category))+1],keyc,sep="")
   }
  
#  print(itemstats[i,])
#  cat("\n")
#  print(itemi,row.names=FALSE)  #Or, use kable as below

  print(kable(itemi,row.names = FALSE,align='cccrrrr'))
  cat("\n")
}
```
## Residual-based item fit statistics
```{r echo=FALSE, comment=NA, message=FALSE}
#print(fit)
kable(fit)
```

## Plot of Infit mean squares
```{r echo=FALSE, comment=NA,fig.height=8,fig.width=6,message=FALSE}
dotchart(fit$Infit, xlim=c(0.5,1.5), labels=fit$item, cex=0.8)
#abline(v=lower,lty=3)
abline(v=upper,lty=3)
```

## The item characteristics curves (observed and expected)
```{r echo=FALSE,results='hide',bunch_o_figs, fig.height=4,fig.width=6, message=FALSE}
plot(mod1,fix.devices=TRUE)
```

